Poker Chips, Earthquakes, and Computation

### 2014-10-11 finaldraft.tex
adding example of earthquake image
improved some wording in the notations section

documentclass[runningheads,a4paper]{llncs}

@@

\begin{definition} We write boards as functions $b$ from $\mathbb{Z}^2 \to \mathbb{Z}_{\geq 0}$.
\end{definition}

@@

\begin{definition} We define $n(i,j)$ to be the set of neighbors of node $(i,j)$
\begin{equation*}
n(i,j) = \{ (i+1, j), (i-1, j), (i, j-1), (i, j+1) \}.
\end{equation*}
\end{definition}

@@

\begin{definition}
An earthquake hits a board $b$ at node $s$, and the resulting board is denoted $E_sb$. If $b(s) \geq 4$, then
\begin{align*}
E_sb(s) &= b(s)-4,\\
E_sb(t) &= b(t)+1 \hspace{.5cm} \forall t \in n(s).\\
\end{align*}
if $b(s) < 4$, the earthquake has no effect and $E_sb = b$. 
\end{definition}

@@

Now that we have formalized the earthquake operator, we make precise the definition of stability.
\begin{definition}
We say that a board is stable if all nodes contain values strictly less than 4. 
\end{definition}
This definition corresponds with the intuitive notion of a process that has stabilized, as stable boards can no longer be affected by earthquake operations.

@@

\begin{definition} 
We say that a board is finite if the total number of chips on it is finite. Otherwise we say a board is infinite. 
\end{definition}

>>>>

\documentclass[runningheads,a4paper]{llncs}

@@

\begin{definition} Boards are functions $b$ from $\mathbb{Z}^2 \to \mathbb{Z}_{\geq 0}$.
\end{definition}

@@

\begin{definition} Let $n(i,j)$ be the set of neighbors of node $(i,j)$
\begin{equation*}
n(i,j) = \{ (i+1, j), (i-1, j), (i, j-1), (i, j+1) \}.
\end{equation*}
\end{definition}

@@

\begin{definition}
Let $E_sb$ be the board that results from an earthquake hitting board $b$ at node $s$. If $b(s) \geq 4$, then
\begin{align*}
E_sb(s) &= b(s)-4,\\
E_sb(t) &= b(t)+1 \hspace{.5cm} \forall t \in n(s).\\
\end{align*}
if $b(s) < 4$, the earthquake has no effect and $E_sb = b$. 
\end{definition}

\begin{figure}
\centering
\subfigure[Board before earthquake.]{\includegraphics[width=0.25\linewidth]{action1.pdf}\label{fig:boardbeforeearthquake}}
\qquad\qquad
\subfigure[Board after earthquake to active square]{\includegraphics[width=0.25\linewidth]{action2.pdf}\label{fig:boardafterequarthquake}}
\caption{Earthquake applied to board. Green signifies active nodes}
\label{fig:earthquakeexample}
\end{figure}

@@

Now that we have formalized the earthquake operator, we make precise the definition of stability.
\begin{definition}
A board is stable if all nodes contain values strictly less than 4. 
\end{definition}
This definition corresponds with the intuitive notion of a process that has stabilized, as stable boards can no longer be affected by earthquake operations.

@@

\begin{definition} 
A board is finite if the total number of chips on it is finite. Otherwise we say a board is infinite. 
\end{definition}
